Video Doesn't Lie

### 2016-04-30 nyu-data-science-reproducibility-16/video-reproducibility.Rmd
One more iframe

<iframe src="http://databrary.org" width=700px height=550px>
</iframe>

@@

<div class="centered">
<video width="640" height="480" controls>
  <source src="http://datavyu.org/user-guide/_static/video/run-a-script.mp4" type="video/mp4">
Your browser does not support the video tag.
</video>
</div>

>>>>

<iframe src="http://databrary.org" width=640px height=480px>
</iframe>

@@

<iframe src="http://datavyu.org/" width=640px height=480px>
</iframe>
